---
output:
  html_document: default
  pdf_document: default
---
# Pre-Processing & Model Selection 

## Data Pre-Processing
From the EDA(Exploratory Data Analysis) and the variable description we found that there were no missing value. However, the variables were of different data type.


| Data Type                  | Variables                                      | Transformation | Technique           |
| -------------------------- | ---------------------------------------------- | -------------- |  -------------------|
| Numerical                  | Wife's age,   Number of children ever born     | Scaling        | Standard Scaling    |
| Ordinal                    | Wife's education, Husband Education,           | Encoding       | Ordinal Encoding    |
|                            | Husband's Occupation,Standard of living Index  |                |                     |
| Binary                     | Wife's religion, Wife working Media Exposure   | None           | Pass through        |


# Finding the best Model:

The target variable,( Contraceptive method used ), has three values:

1=No-use, 2=Long-term, 3=Short-term

During the EDA we found that there was a class imbalance problem. Hence, we combined 2=Long-term, 3=Short-term into one class and it was given a value of 1.  1=No-use was given a value of 0.
So now we have  0=No-use : 445 observations, 1=use : 586 observations. Now, it is binary classification problem. The model we tried:

1. Decision Tree
2. kNN
3. Logistic Regression
4. RBF SVC

## Results of Cross Validation
From the Figure \@ref(fig:crossVal) It can be clearly seen than the RBF SVC is giving us the best score on both train and cross val dataset.

```{r crossVal, echo=FALSE, fig.cap="Cross Validation Result (Score for Accuracy)", out.width = '50%'}
cross_val <- read.csv("../results/val_score_results.csv") 
knitr::kable(cross_val, "pipe")
```


## Hyper-Parameter Optimization
Since the performance of RBF SVC was the best we took it further for hyper-parameter tuning \@ref(fig:hyperparam). We found that the best parameters are:
C= 10.0
gamma = 0.01

```{r hyperparam, echo=FALSE, fig.cap="Hyperparameter Selection", out.width = '100%'}
hyperparameter <- read.csv("../results/val_score_results.csv") 
knitr::kable(hyperparameter, "pipe")
```
